Parallel Monte Carlo Synthetic Acceleration Methods for Discrete Transport Problems

### 2013-09-04 doc/dissertation/presentation/defense.tex
adding some more corrections to slides

{\tiny  \begin{table}[h!]
    \begin{center}
      \begin{tabular}{cccccc}\hline\hline
        \multicolumn{1}{c}{}& 
        \multicolumn{1}{c}{}& 
        \multicolumn{1}{c}{}& 
        \multicolumn{1}{c}{$SP_N$ Order}& 
        \multicolumn{1}{c}{}& 
        \multicolumn{1}{c}{} \\
        &   & \textbf{1} & \textbf{3} & \textbf{5} & \textbf{7}  \\
        & \textbf{0} & 0.0647 & 0.1275 & 0.1449 & 0.1514 \\
        & \textbf{1} & 0.0686 & 0.1338 & 0.1484 & 0.1547 \\
        $P_N$ Order & \textbf{3} & 0.0687 & 0.1399 & 0.1582 & 0.1625 \\
        & \textbf{5} & 0.0692 & 0.1399 & 0.1582 & 0.1657 \\
        & \textbf{7} & 0.0678 & 0.1393 & 0.1624 & 0.166 \\
        %%
        \hline\hline
      \end{tabular}
    \end{center}
    \caption{\textbf{Spectral radius results for the block Jacobi
        preconditioned iteration matrix with 10 energy groups and full
        downscatter for sample problem.}}
    \label{tab:group10dsbj}
  \end{table}
}

@@

      {\tiny
      \begin{table}[h!]
        \begin{center}
          \begin{tabular}{lccc}\hline\hline
            \multicolumn{1}{l}{Solver}&
            \multicolumn{1}{c}{1 Group}&
            \multicolumn{1}{c}{2 Groups}&
            \multicolumn{1}{c}{4 Groups}\\
            \hline
            BiCGStab-ILUT & 11.6 & 11.6 & 12.4 \\ 
            GMRES-ILUT & 18.1 & 17.9 & 18.9 \\
            MCSA-ILUT-R-C & 14.6 & 15.4 & 17.6 \\
            MCSA-ILUT-MR-C & 16.0 & 17.1 & 23.7 \\
            MCSA-ILUT-R-EV & 18.3 & 19.4 & 16.8 \\
            MCSA-ILUT-MR-EV & 19.6 & 22.4 & 17.5 \\
            Richardson-ILUT & 60.9 & 60.4 & 63.4 \\
            %%
            \hline\hline
          \end{tabular}
        \end{center}
        \caption{ Average number of linear solver iterations per
          eigenvalue iteration.}
      \end{table}
      }

@@

      \begin{itemize}
      \item Weaker preconditioning at \sn{1}{-5} case
      \item Forcing term method adapts to nonlinear convergence
      \item Constant forcing term for \sn{1}{-6} case
      \end{itemize}

@@

      \begin{itemize}
      \item Forcing term selection can significantly modify nonlinear
        convergence
        \medskip
      \item $\eta_k = \gamma \Big(
        \frac{||\ve{F}(\ve{u}_k)||}{||\ve{F}(\ve{u}_{k-1})||}
        \Big)^{\alpha}$
      \end{itemize}

@@

%%---------------------------------------------------------------------------%%
\begin{frame}{Iterative Performance Summary}

@@

    \begin{column}{0.5\textwidth}
      \begin{figure}[htpb!]
        \begin{center}
          \scalebox{0.75}{ \input{ddnu_example.pdftex_t} }
        \end{center}
        \caption{\small \sl Domain decomposition example illustrating
          how domain-to-domain transport creates communication costs.}
      \end{figure}
    \end{column}
  \end{columns}

@@

    \begin{column}{0.5\textwidth}
      \begin{figure}[htpb!]
        \begin{center}
          \scalebox{0.75}{ \input{msod_example.pdftex_t} }
        \end{center}
        \caption{\small \sl Overlapping domain example illustrating
          how domain overlap can reduce communication costs.}
      \end{figure}
    \end{column}

@@

@@

      \begin{figure}[htpb!]
        \begin{center}
          \scalebox{0.25}{ \input{msod_construction.pdftex_t} }
        \end{center}
        \caption{\small \sl MSOD construction.}
      \end{figure}

@@

      \begin{figure}[htpb!]
        \begin{center}
          \scalebox{0.25}{ \input{msod_tally.pdftex_t} }
        \end{center}
        \caption{\small \sl MSOD tally reduction.}
      \end{figure}

@@

>>>>

{\tiny  \begin{table}[h!]
    \begin{center}
      \begin{tabular}{cccccc}\hline\hline
        \multicolumn{1}{c}{}& 
        \multicolumn{1}{c}{}& 
        \multicolumn{1}{c}{}& 
        \multicolumn{1}{c}{$SP_N$ Order}& 
        \multicolumn{1}{c}{}& 
        \multicolumn{1}{c}{} \\
        &   & \textbf{1} & \textbf{3} & \textbf{5} & \textbf{7}  \\
        & \textbf{0} & 0.0647 & 0.1275 & 0.1449 & 0.1514 \\
        & \textbf{1} & 0.0686 & 0.1338 & 0.1484 & 0.1547 \\
        $P_N$ Order & \textbf{3} & 0.0687 & 0.1399 & 0.1582 & 0.1625 \\
        & \textbf{5} & 0.0692 & 0.1399 & 0.1582 & 0.1657 \\
        & \textbf{7} & 0.0678 & 0.1393 & 0.1624 & 0.166 \\
        %%
        \hline\hline
      \end{tabular}
    \end{center}
    \caption{Spectral radius results for the block Jacobi
      preconditioned iteration matrix with 10 energy groups and full
      downscatter for sample problem.}
    \label{tab:group10dsbj}
  \end{table}
}

@@

      {\tiny
      \begin{table}[h!]
        \begin{center}
          \begin{tabular}{lccc}\hline\hline
            \multicolumn{1}{l}{Solver}&
            \multicolumn{1}{c}{1 Group}&
            \multicolumn{1}{c}{2 Groups}&
            \multicolumn{1}{c}{4 Groups}\\
            \hline
            BiCGStab-ILUT & 11.6 & 11.6 & 12.4 \\ 
            GMRES-ILUT & 18.1 & 17.9 & 18.9 \\
            MCSA-ILUT-R-C & 14.6 & 15.4 & 17.6 \\
            MCSA-ILUT-MR-C & 16.0 & 17.1 & 23.7 \\
            MCSA-ILUT-R-EV & 18.3 & 19.4 & 16.8 \\
            MCSA-ILUT-MR-EV & 19.6 & 22.4 & 17.5 \\
            Richardson-ILUT & 60.9 & 60.4 & 63.4 \\
            %%
            \hline\hline
          \end{tabular}
        \end{center}
        \caption{Average number of linear solver iterations per
          eigenvalue iteration.}
      \end{table}
      }

@@

      \small{
        \begin{itemize}
        \item Weaker preconditioning at Ra=\sn{1}{-5} case
          \medskip
        \item $\eta_k = \gamma \Big(
          \frac{||\ve{F}(\ve{u}_k)||}{||\ve{F}(\ve{u}_{k-1})||}
          \Big)^{\alpha}$
          \medskip
        \item Constant forcing term for Ra=\sn{1}{-6} case
          \medskip
        \item RDA applied in all cases
        \end{itemize}
      }

@@

      \small{
        \begin{itemize}
        \item Forcing term selection can significantly modify nonlinear
          convergence
        \item Newton-Krylov had larger forcing terms for Re=100,300,500
        \item At Re=700, MCSA histories doubled and RDA fill increased
          from 200 to 300
        \end{itemize}
      }

@@

%%---------------------------------------------------------------------------%%
\begin{frame}{FANM Iterative Performance Summary}

@@

    \begin{column}{0.5\textwidth}
      \begin{figure}[htpb!]
        \begin{center}
          \scalebox{0.75}{ \input{ddnu_example.pdftex_t} }
        \end{center}
        \caption{\small Domain decomposition example illustrating
          how domain-to-domain transport creates communication costs.}
      \end{figure}
    \end{column}
  \end{columns}

@@

    \begin{column}{0.5\textwidth}
      \begin{figure}[htpb!]
        \begin{center}
          \scalebox{0.75}{ \input{msod_example.pdftex_t} }
        \end{center}
        \caption{\small Overlapping domain example illustrating how
          domain overlap can reduce communication costs.}
      \end{figure}
    \end{column}

@@

%%---------------------------------------------------------------------------%%
\begin{frame}[fragile]{Multiple-Set Overlapping-Domain Decomposition}

@@

      \begin{figure}[htpb!]
        \begin{center}
          \scalebox{0.2}{ \input{msod_construction.pdftex_t} }
        \end{center}
        \caption{\small MSOD construction.}
      \end{figure}

@@

      \begin{figure}[htpb!]
        \begin{center}
          \scalebox{0.2}{ \input{msod_tally.pdftex_t} }
        \end{center}
        \caption{\small MSOD tally reduction.}
      \end{figure}

@@

    \begin{algorithm}[H]
      \begin{algorithmic}[1]
        \tiny
        \STATE build MSOD domain
        \STATE build Monte Carlo source
        \STATE build Monte Carlo tally
        \STATE perform parallel Neumann-Ulam transport in each set
        \STATE combine set tallies
        \STATE combine block tallies
      \end{algorithmic}
      \caption{MSOD Transport Sequence}
    \end{algorithm}
